### 2011-08-01 doc/theses/svirec/kap2.tex
thesis fixing

\section{XML Trees and DTDs}
\begin{define}[Tree]
Being given an alphabet of nodes $\mathbb{N}$ and an alphabet of node labels $\Sigma$, a {\sl tree} $T$ over $\mathbb{N}$ and $\Sigma$ is a tuple $(r_T, N_T, E_T, \lambda_T)$, where $N_T \subseteq \mathbb{N}$ is the set of nodes, $\lambda_T : N_T \to \Sigma$ is a node labelling function, $r_T \in N_T$ is the distinguished root of $T$, and $E_T \subseteq N_T \times N_T$ is a set of edges such that starting from any node $n_i \in N_T$ it is possible to reach any other node $n_j \in N_T$, walking through a sequence of edges $e_1,\dots,e_k$ which are connected and acyclic.
\end{define}

@@

\begin{define}[XML Integrity Constraint]\label{integConstr}
An XML constraint is a formula of the form: $$(\forall X)[\Phi(X)\supset (\exists Y_1)\Psi_1(X,Y_1) \lor \dots \lor (\exists Y_k)(X,Y_k)]$$
where $X,Y_1,\dots, Y_k$ denote distinct sets of universally and existentially quantified variables, $\Phi(X)$ and $\Phi(X) \land \Psi_i(X, Y_i) (\forall i \in [1..k])$ are safe conjunctions of built-in and tree atoms.\qed
\end{define}

@@

\begin{figure}[H]
    \centering\includegraphics[width=\textwidth]{tuples}
	\caption{Two tree tuples of the XML tree in Fig. \ref{example1}} \label{tuples}
\end{figure}

\begin{figure}[H]
    \centering
    \subfloat[]{\label{nottuple1}\includegraphics[scale=0.6]{nottuples1}}
    \subfloat[]{\label{nottuple2}\includegraphics[scale=0.6]{nottuples2}}
	\caption{Two subtrees of the XML tree in Fig. \ref{example1} which are not tree tuples}
    \label{nottuples}
\end{figure}

>>>>

\section{XML Trees and DTDs}
\begin{define}[Tree]
Being given an alphabet of nodes $\mathbb{N}$ and an alphabet of node labels $\Sigma$, a {\sl tree} $T$ over $\mathbb{N}$ and $\Sigma$ is a tuple $(r_T, N_T, E_T, \lambda_T)$, where $N_T \subseteq \mathbb{N}$ is the set of nodes, $\lambda_T : N_T \to \Sigma$ is a node labelling function, $r_T \in N_T$ is the distinguished root of $T$, and $E_T \subseteq N_T \times N_T$ is a set of edges such that starting from any node $n_i \in N_T$ it is possible to reach any other node $n_j \in N_T$, walking through a sequence of edges $e_1,\dots,e_k$ which are connected and acyclic.\qed
\end{define}

@@

\begin{define}[XML Integrity Constraint]\label{integConstr}
An {\sl XML constraint} is a formula of the form: $$(\forall X)[\Phi(X)\supset (\exists Y_1)\Psi_1(X,Y_1) \lor \dots \lor (\exists Y_k)(X,Y_k)]$$
where $X,Y_1,\dots, Y_k$ denote distinct sets of universally and existentially quantified variables, $\Phi(X)$ and $\Phi(X) \land \Psi_i(X, Y_i) (\forall i \in [1..k])$ are safe conjunctions of built-in and tree atoms.\qed
\end{define}

@@

\begin{figure}[H]
    \centering\includegraphics[width=\textwidth]{tuples}
	\caption[Two tree tuples of the XML tree]{Two tree tuples of the XML tree in Fig. \ref{example1}} \label{tuples}
\end{figure}

\begin{figure}[H]
    \centering
    \subfloat[]{\label{nottuple1}\includegraphics[scale=0.6]{nottuples1}}
    \subfloat[]{\label{nottuple2}\includegraphics[scale=0.6]{nottuples2}}
	\caption[Two subtrees of the XML tree]{Two subtrees of the XML tree in Fig. \ref{example1} which are not tree tuples}
    \label{nottuples}
\end{figure}

### 2011-08-01 doc/theses/svirec/kap3.tex
thesis fixing

To be able to resolve the problem of functional dependency violations in XML document, the authors try to introduce the concept of functional dependencies based on those defined for relational databases. The concept of a tree tuple and functional dependency was introduced in definition \ref{treeTuple} and \ref{fd1}.

@@

\begin{define}[Weak satisfiability]\label{weakSatisf}
Let $RXT = \langle T, \delta, \varrho \rangle$ be an R-XML tree conforming a DTD $D$, and $f: S \rightarrow p$ be a functional dependency. We say that $RXT$ weakly satisfies $f$ ($RXT \models_w f$) if one of the following conditions holds:
\begin{enumerate}
	\item $\langle T, \delta \rangle \models f$;
    \item for each pair of tuples $t_1$, $t_2$ of $RXT$ one of the following holds:
    \begin{enumerate}
    	\item there exists a path $p_i \in S$ such that: \\
$(\varrho(p_i(t_1)) = false) \lor (\varrho(p_i(t_2)) = false)$;
        \item $(\varrho(p(t_1)) = false) \lor (\varrho(p(t_2)) = false)$.\qed
    \end{enumerate}
\end{enumerate}
\end{define}

@@

\begin{define}[Composition of $\delta$ functions]\label{compDelta}
The composition of two functions $\delta_1$ and $\delta_2$ asssociating values to leaf nodes is
\begin{displaymath}
    \delta_1 \cdot \delta_2(n) =
        \begin{cases}
            \delta_1(n) & \text{if $\delta_1(n)$ is defined over $n$,}\\
            \delta_2(n) & \text{otherwise (i.e. $\delta_1(n)$ is not defined over $n$).}
        \end{cases}
\end{displaymath}\qed
\end{define}

\begin{define}[Composition of $\varrho$ functions]\label{compVarrho}
The composition of two reliability functions $\varrho_1$ and $\varrho_2$ asssociating a boolean value to nodes is $$\varrho_1 \cdot \varrho_2(n) = \varrho_1(n)\ AND\ \varrho_2(n).$$\qed
\end{define}

@@

\begin{define}[Minimal Repair]
Let $RXT = \langle T, \delta, \varrho \rangle$ be an R-XML tree conforming DTD $D$, $\mathcal{FD}$ a set of functional dependencies and $R_1 = \langle \delta_1, \varrho_1 \rangle$, $R_2 = \langle \delta_2, \varrho_2 \rangle$ two repairs for $RXT$. We say that $R_1$ is smaller than $R_2$ ($R_1 \preceq R_2$) if $Updated_{\delta_1}(N_T)\ \cup\ False_{\delta_1}(N_T) \subseteq Updated_{\delta_2}(N_T)\ \cup\ False_{\delta_2}(N_T)$ and $False_{\delta_1}(N_T) \subseteq False_{\delta_2}(N_T)$. Repair $R$ is minimal if there is no repair $R' \neq R$ such that $R' \preceq R$.\qed
\end{define}

@@

\begin{define}[Repair]
Given an XML tree $T$, a DTD $D$ and a set of integrity constraints $IC$ (Definition \ref{integConstr}), a set of update operations $R$ is said to be a repair of $T$ (with respect to $D$ and $IC$) if $R(T) \models IC$, where $R(T)$ is application of consistent set of updates $R$ to $T$, $R(T)$ conforms $D$ and $\not \exists R' \sqsubset R$ such that $R'(T) \models IC$ and $R'(T)$ conforms $D$.
\end{define}

>>>>

To be able to resolve the problem of functional dependency violations in XML document, the authors try to introduce the concept of functional dependencies based on those defined for relational databases. The concept of a tree tuple and functional dependency was introduced in Definition \ref{treeTuple} and \ref{fd1}.

@@

\begin{define}[Weak satisfiability]\label{weakSatisf}
Let $RXT = \langle T, \delta, \varrho \rangle$ be an R-XML tree conforming a DTD $D$, and $f: S \rightarrow p$ be a functional dependency. We say that $RXT$ {\sl weakly satisfies} $f$ ($RXT \models_w f$) if one of the following conditions holds:
\begin{enumerate}
	\item $\langle T, \delta \rangle \models f$;
    \item for each pair of tuples $t_1$, $t_2$ of $RXT$ one of the following holds:
    \begin{enumerate}
    	\item there exists a path $p_i \in S$ such that: \\
$(\varrho(p_i(t_1)) = false) \lor (\varrho(p_i(t_2)) = false)$;
        \item $(\varrho(p(t_1)) = false) \lor (\varrho(p(t_2)) = false)$.\qed
    \end{enumerate}
\end{enumerate}
\end{define}

@@

\begin{define}[Composition of $\delta$ functions]\label{compDelta}
The {\sl composition} of two functions $\delta_1$ and $\delta_2$ asssociating values to leaf nodes is
\begin{displaymath}
    \delta_1 \cdot \delta_2(n) =
        \begin{cases}
            \delta_1(n) & \text{if $\delta_1(n)$ is defined over $n$,}\\
            \delta_2(n) & \text{otherwise (i.e. $\delta_1(n)$ is not defined over $n$).}
        \end{cases}
\end{displaymath}\qed
\end{define}

\begin{define}[Composition of $\varrho$ functions]\label{compVarrho}
The {\sl composition} of two reliability functions $\varrho_1$ and $\varrho_2$ asssociating a boolean value to nodes is $$\varrho_1 \cdot \varrho_2(n) = \varrho_1(n)\ AND\ \varrho_2(n).$$\qed
\end{define}

@@

\begin{define}[Minimal Repair]
Let $RXT = \langle T, \delta, \varrho \rangle$ be an R-XML tree conforming DTD $D$, $\mathcal{FD}$ a set of functional dependencies and $R_1 = \langle \delta_1, \varrho_1 \rangle$, $R_2 = \langle \delta_2, \varrho_2 \rangle$ two repairs for $RXT$. We say that $R_1$ is smaller than $R_2$ ($R_1 \preceq R_2$) if $Updated_{\delta_1}(N_T)\ \cup\ False_{\delta_1}(N_T) \subseteq Updated_{\delta_2}(N_T)\ \cup\ False_{\delta_2}(N_T)$ and $False_{\delta_1}(N_T) \subseteq False_{\delta_2}(N_T)$. Repair $R$ is {\sl minimal} if there is no repair $R' \neq R$ such that $R' \preceq R$.\qed
\end{define}

@@

\begin{define}[Repair]
Given an XML tree $T$, a DTD $D$ and a set of integrity constraints $IC$ (Definition \ref{integConstr}), a set of update operations $R$ is said to be a {\sl repair} of $T$ (with respect to $D$ and $IC$) if $R(T) \models IC$, where $R(T)$ is application of consistent set of updates $R$ to $T$, $R(T)$ conforms $D$ and $\not \exists R' \sqsubset R$ such that $R'(T) \models IC$ and $R'(T)$ conforms $D$.
\end{define}
